Why does preregistration increase the persuasiveness of evidence? A Bayesian rationalization

### 2025-06-24 manuscript.Rmd
accepted in Metapsychology

  Submitted to *Meta-Psychology*. Participate in open peer review by sending an email to open.peer.reviewer@gmail.com. The full editorial process of all articles under review at Meta-Psychology can be found following this link:  
  https://tinyurl.com/mp-submissions  
  You will find this preprint by searching for the first author's name.

---

>>>>

  This preprint has now been peer reviewed and accepted for publication in Meta-Psychology.
---
